The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190611.tex
CIV tex/ tidy up

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
%Aaron M. Meisner$^{7,8}$, Roberto J. Assef$^{9}$, Arjun Dey$^{10}$, Andrew J. Drake$^{11}$, \newauthor Hyunsung D. Jun$^{12}$, Dustin Lang$^{13,14,15}
\\
% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2018}

@@

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc imperdiet facilisis volutpat. Phasellus ultricies justo a ante bibendum porta. Nulla varius convallis risus in tincidunt. Vivamus sit amet massa non dui volutpat porttitor. Donec imperdiet mauris non risus commodo tempor. Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus. Vestibulum vel ante elementum nisl feugiat sollicitudin. Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
%%
Nulla ante mauris, mattis a tristique eu, pharetra eget erat. Cras et ultrices lectus. Praesent augue erat, commodo ac malesuada vel, mattis ac nisi. Quisque eu vehicula urna, in fringilla nunc. Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus. Sed cursus scelerisque dapibus. Proin a bibendum neque, sit amet aliquet arcu. Vivamus in eros lectus. Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc. Donec egestas tellus vel urna interdum tincidunt. Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est. Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi. Aliquam non lobortis tellus. Morbi vulputate porta placerat. Quisque dapibus pretium arcu eget tempor. Aenean in tincidunt nisi. Aenean interdum congue enim.
\end{abstract}

@@

For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the
standard UV/blue continnum slope increases in flux. 
For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
the UV/blue continuum diminshes and the shape of \lya changes.

\subsection{Literature Search}
\citet{Baldwin1977}...
Since the discovery of an anticorrelation between the equivalent width $W_{\lambda}$ of the \civ $\lambda$1549 emission line and the continuum luminosity $L$ by Baldwin (1977),

%\includegraphics[]{../../../../../Users/npr1/Downloads/mnras0409-0591.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/681-689.pdf}

%\includegraphics[]{../../../../../Users/npr1/Downloads/1991ApJ___371L__51C.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1992A+AS___96__613D.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1993IAUS__155___94D.pdf}
%[]{../../../../../Users/npr1/Downloads/1993ApJ___415__563W.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___423__131B.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}

See e.g., \citet{HamannFerland1999} and \citet{Sulentic2000_ARAA} for reviews of 
elemental abundances and phenomenology of broad emission lines in 
AGN.

\citet{Dietrich2002}

\citet{Croom2002}

\citet{Hamann2002}

@@

%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}

%%\citet{Punsly2010}
%% Punsly 2010
%% Astrophysical Journal, 713, 232
%% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES
%%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}

\citet{Bian2012}

\citet{Sun2015} , ApJ, 811, 42
%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}

@@

\citet{Denney2016} investigate the dependence on data quality of quasar properties
measured from the C IV emission line region at high redshifts.  Our
measurements come from 32 epochs of Sloan Digital Sky Survey
Reverberation Mapping Project spectroscopic observations of 482 $z >
1.46$ quasars. We compare the differences between measurements made
from the single-epoch (SE) and coadded spectra, focusing on the \civ
$\lambda$1549 emission line because of its importance for studies of
high-redshift quasar demographics and physical properties, including
black hole masses. In addition to statistical errors increasing (by
factors of $\sim2-4$), we find increasing systematic offsets with
decreasing signal-to-noise ratio (S/N).

%%\citet{Cracco2016}

\citet{Ge2016}

\citep{Tammour2016} use the K-means unsupervised clustering algorithm 
to study a sample of quasar UV spectra from the 10th Data Release of the Sloan Digital Sky Survey
\citep[SDSS-DR10Q; ][]{Paris2014}.

@@

%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}

\citet{Sulentic2017} find that:

{\it (i):} \civ outflows become stronger and more frequent at higher-$z$ in sources with 2-4 dex higher luminosity than low-$z$ quasars. The emission component associated with the outflow becomes a dominant source of line broadening, and confirms that the full \civ profile is not a useful virial estimator of black hole mass for most sources. 
{\it (ii):} We show evidence that the Civ outflows are driven by $L/LEdd$ rather than source luminosity. A clear dependence of \civ blueshifts on Eddington ratio is observed while a weaker trend is observed with source luminosity that becomes appreciable only over a wide luminosity range (4–5 dex). Large shifts ($c(\frac{1}{2}) \lesssim -1000 km s^{-1}$) are apparently possible above a threshold $L/L_{\rm Edd} \approx 0.2\pm0.1$. 
{\it (iii):} The relations between $c(\frac{1}{2})$ and $L/L_{\rm Edd}$ and $L$ are consistent with a radiation-driven outflow, and the largest shifts may support the existence of an optically thick ADAF in at least some of the Pop. A sources.

\citet{Martinez-Aldama2018} 
present a sample of 19 quasar satisfying the 
4D eigenvector 1 \citep[4DE1; ][]{Sulentic2000, Marziani2001} 
selection criteria for finding high redshift highly accretors xA sources. 
and show that this sample is likely radiating close to the Eddington limit 
$(L/L_{\rm Edd} \geq 0.2)$. 
FWHM, centroid at half intensity $c(\frac{1}{2})$

\subsection{The Baldwin Effect}
\input{Beff}

\subsection{Carbon IV}
Table~\ref{tab:civ_configs} from 
Atomic Line List version: 2.05b21  
%%Version 2.05b21 of the line list was created: Nov 7, 2017.
\citep{Tunklev1997} \\

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\subsection{Selection/Identification}

@@

\subsection{Check Hamann 2017}
\citet{Hamann2017} carry out a deep investigation into Extremely Red Quasars \citep[ERQs;][]{Ross2015, Zakamska2016} using the SDSS-III BOSS dataset. One product of that investigation is a new catalogue of \civ and \nv emission-line data for 216 188 BOSS quasars. %% to characterize the ERQ line properties further.

\input{Ham17_clqs}

@@

%\subsection{J1504+1029}
%SDSS J150425.0+102939.2

\subsection{J2344-0039}
SDSS J234423.8-003950.2

\subsection{Richards et al. (2011)}
98,715 objects in %actual input (public.gtr.DR7qsosHW10pub2) and output tables 
public.gtr.dr7qsos\_c4b\_HW10pub2n\_big from SDSS CasJobs.

588018055127629913

\subsubsection{Lines from SDSS database}
\civ  $\lambda$1549.479 \\
2799 $\lambda$2799.116  \\
1909 $\lambda$1908.734 \\

\subsection{Multi-wavelength properties}
MIR \\

Radio. \\ 
J2228+2201 is not in the area currently covered by the FIRST catalog.

Searching the FIRST catalog for sources within 10.0000 arcsec of 16 38 52.930 +28 27 07.70 (J2000). 
Map RMS at search position is 0.133 mJy/beam. 
Catalog detection limit (including CLEAN bias) at source position is 0.91 mJy/beam
No sources found within 10.0000 arcsec

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{In the context of CLQs at lower-$z$}

@@

\bibliographystyle{mnras}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}

>>>>

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
% Matthew Graham$^{5}$
% K. E. Saavik Ford$^{2,3,4}$, 
% Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
\\
%% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2019}

@@

\begin{abstract}
%% 190 words of 'lorem ipsum' (200 words Abstract total for MNRAS Letters)
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc imperdiet facilisis volutpat. Phasellus ultricies justo a ante bibendum porta. Nulla varius convallis risus in tincidunt. Vivamus sit amet massa non dui volutpat porttitor. Donec imperdiet mauris non risus commodo tempor. Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus. Vestibulum vel ante elementum nisl feugiat sollicitudin. Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
%%
Nulla ante mauris, mattis a tristique eu, pharetra eget erat. Cras et ultrices lectus. Praesent augue erat, commodo ac malesuada vel, mattis ac nisi. Quisque eu vehicula urna, in fringilla nunc. Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus. Sed cursus scelerisque dapibus. Proin a bibendum neque, sit amet aliquet arcu. Vivamus in eros lectus. Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc. Donec egestas tellus vel urna interdum tincidunt. Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est. Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi. Aliquam non lobortis tellus. Morbi vulputate porta placerat. Quisque dapibus pretium arcu eget tempor. Aenean in tincidunt nisi. Aenean interdum congue enim.
\end{abstract}

@@

For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the standard UV/blue continuum slope increases in flux. For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, the UV/blue continuum diminishes and the shape of \lya changes.

%% \subsection{Literature Search}

@@

%% Punsly 2010
%% Astrophysical Journal, 713, 232
%% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES

\citet{Wilhite2005} and especially \citet{Wilhite2006}

\citet{Wilhite2008} also...

@@

@@

%\includegraphics\includegraphics[]{../../../../../Users/npr1/Downloads/Richards_2011_AJ_141_167.pdf}

%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}

%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}

\citet{Denney2016}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Denney_2016_ApJS_224_14.pdf}
investigate the dependence on data quality of quasar properties
measured from the C IV emission line region at high redshifts.  Our
measurements come from 32 epochs of Sloan Digital Sky Survey
Reverberation Mapping Project spectroscopic observations of 482 $z >
1.46$ quasars. We compare the differences between measurements made
from the single-epoch (SE) and coadded spectra, focusing on the \civ
$\lambda$1549 emission line because of its importance for studies of
high-redshift quasar demographics and physical properties, including
black hole masses. In addition to statistical errors increasing (by
factors of $\sim2-4$), we find increasing systematic offsets with
decreasing signal-to-noise ratio (S/N).

%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}

%\includegraphics[]{../../../../../Users/npr1/Downloads/mnras0409-0591.pdf}
%%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/681-689.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___423__131B.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1992A+AS___96__613D.pdf}
%%\includegraphics[]{../../../../../Users/npr1/Downloads/1993IAUS__155___94D.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1991ApJ___371L__51C.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
%[]{../../../../../Users/npr1/Downloads/1993ApJ___415__563W.pdf}

%%\subsection{Carbon IV}
Table~\ref{tab:civ_configs} from 
Atomic Line List version: 2.05b21  
%%Version 2.05b21 of the line list was created: Nov 7, 2017.
\citep{Tunklev1997} \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}
\section{Data}
\subsection{Selection/Identification}

@@

@@

\subsection{Multi-wavelength properties}
MIR \\
Radio \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Even with nearly a change of a decade in the continuum flux, no 
no change is seen in the flux of the \civ line flux \citet[e.g. Figure 6 in ][]{Hawkins2011}.

\citep{Wilhite2006} for SDSS...

\subsection{In the context of CLQs at lower-$z$}

@@

\bibliographystyle{mnras}
\bibliography{tester_mnras}
